The {TestIdeals} package for \emph{Macaulay2}

### 2019-04-24 Fsing/TestIdealsPaper/TestIdeals.tex

Again, consider the maps $T^e : \omega_{R^{1/p^e}} \to \omega_R$ we have considered throughout this section.  It is a theorem of Hartshorne-Speiser, Lyubeznik, and Gabber \cite{HartshorneSpeiserLocalCohomologyInCharacteristicP,LyubeznikFModulesApplicationsToLocalCohomology,Gabber.tStruc} that the descending images
\begin{equation}\label{eq: descending images}
\omega_R \supseteq T(\omega_{R^{1/p}}) \supseteq \dots \supseteq T^e(\omega_{R^{1/p^e}}) \supseteq T^{e+1}(\omega_{R^{1/p^{e+1}}}) \supseteq \cdots
\end{equation}
stabilize for $e \gg 0$.
The function \texttt{HSLGModule} computes the stable submodule in this chain, called the \emph{HSLG module}, and returns a list containing the following items:
\begin{enumerate}[(1)]
   \item The HSLGmodule;
   \item The canonical module, embedded (non-uniquely) as an ideal;
   \item The element $u$ representing the map on the canonical module (see
   \autoref{subsec.DualToFrobeniusOnQuotientRings});
   \item The value of $e > 0$ at which the descending images in \eqref{eq: descending images} stabilize.  This is sometimes also called the HSLG number of the canonical module as a Cartier module.
\end{enumerate}

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/3[x,y,z]/(x^3 + y^4 + z^5);
i2 : L = HSLGModule R;
i3 : L#0
                          2        2   3
o3 = ideal (0, y*z, x*z, y , x*y, x , z )
o3 : Ideal of R
i4 : L#1
o4 = ideal 1
o4 : Ideal of R
i5 : L#3
o5 = 1
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/2[x,y,z];
i2 : f = x^3 + y^2*z + y*z^2;
i3 : frobeniusPower(1/2, ideal f)
o3 = ideal (x, y, z)
o3 : Ideal of R
i4 : u=f^3;
i5 : frobeniusPower(1/4, ideal u)
o6 = ideal (x, y, z)
o6 : Ideal of R
i7 : ((HSLGModule(1, f))#3) + 1
o7 : 2
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/11[x,y,z];
i2 : f = y^2*z^3 - x^5 - 2*z^5;
i3 : frobeniusPower(1/11, ideal f^10)
             2        3
o6 = ideal (z , x*z, x )
o3 : Ideal of R
i5 : frobeniusPower(1/121, ideal f^120)
             2        3
o6 = ideal (z , x*z, x )
o6 : Ideal of R
i7 : ((HSLGModule(1, f))#3) + 1
o7 : 2
\end{MyVerbatim}
}\medskip

>>>>

Again, consider the maps $T^e : \omega_{R^{1/p^e}} \to \omega_R$ we have considered throughout this section.  It is a theorem of Hartshorne-Speiser, Lyubeznik, and Gabber \cite{HartshorneSpeiserLocalCohomologyInCharacteristicP,LyubeznikFModulesApplicationsToLocalCohomology,Gabber.tStruc} that the descending images
\begin{equation}\label{eq: descending images}
\omega_R \supseteq T(\omega_{R^{1/p}}) \supseteq \dots \supseteq T^e(\omega_{R^{1/p^e}}) \supseteq T^{e+1}(\omega_{R^{1/p^{e+1}}}) \supseteq \cdots
\end{equation}
stabilize for $e \gg 0$.
The function \texttt{FPureModule} computes the stable submodule in this chain, called the \emph{HSLG module}, and returns a list containing the following items:
\begin{enumerate}[(1)]
   \item The HSLGmodule;
   \item The canonical module, embedded (non-uniquely) as an ideal;
   \item The element $u$ representing the map on the canonical module (see
   \autoref{subsec.DualToFrobeniusOnQuotientRings});
   \item The value of $e > 0$ at which the descending images in \eqref{eq: descending images} stabilize.  This is sometimes also called the HSLG number of the canonical module as a Cartier module.
\end{enumerate}

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/3[x,y,z]/ideal( x^3 + y^4 + z^5 );
i2 : L = FPureModule R;
i3 : L#0
                          2        2   3
o3 = ideal (0, y*z, x*z, y , x*y, x , z )
o3 : Ideal of R
i4 : L#1
o4 = ideal 1
o4 : Ideal of R
i5 : L#3
o5 = 1
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/2[x,y,z];
i2 : f = x^3 + y^2*z + y*z^2;
i3 : frobeniusPower(1/2, ideal f)
o3 = ideal (x, y, z)
o3 : Ideal of R
i4 : u=f^3;
i5 : frobeniusPower(1/4, ideal u)
o6 = ideal (x, y, z)
o6 : Ideal of R
i7 : ((FPureModule(1, f))#3) + 1
o7 : 2
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/11[x,y,z];
i2 : f = y^2*z^3 - x^5 - 2*z^5;
i3 : frobeniusPower(1/11, ideal f^10)
             2        3
o6 = ideal (z , x*z, x )
o3 : Ideal of R
i5 : frobeniusPower(1/121, ideal f^120)
             2        3
o6 = ideal (z , x*z, x )
o6 : Ideal of R
i7 : ((FPureModule(1, f))#3) + 1
o7 : 2
\end{MyVerbatim}
}\medskip
